---
title: "ggPlot Notes"
format: html
editor: source
---

## ggPlot!! FUN FUN FUN
https://www.cedricscherer.com/2019/08/05/a-ggplot2-tutorial-for-beautiful-plotting-in-r/#data

## Intro
a good recource to use is Beautiful plotting in R: A ggplot2 cheatsheet by Zev Ross http://zevross.com/blog/2014/08/04/beautiful-plotting-in-r-a-ggplot2-cheatsheet-3/

```{r}
# install CRAN packages

install.packages(
  c("ggplot2", "tibble", "tidyr", "forcats", "purrr", "prismatic", "corrr", 
    "cowplot", "ggforce", "ggrepel", "ggridges", "ggsci", "ggtext", "ggthemes", 
    "grid", "gridExtra", "patchwork", "rcartocolor", "scico", "showtext", 
    "shiny", "plotly", "highcharter", "echarts4r")
)

# install from GitHub since not on CRAN
install.packages("devtools")
devtools::install_github("JohnCoene/charter")
```
## The Dataset

```{r}
chic <- readr::read_csv("https://cedricscherer.com/data/chicago-nmmaps-custom.csv")

tibble::glimpse(chic)
head(chic, 10)
```
## The {ggplot2} Package

**ggplot2 Overview:**

*   ggplot2 is a graphics system for creating visuals based on The Grammar of Graphics.

*   It allows for declarative creation of graphics.

*   Users provide data and specify mappings, and ggplot2 handles the details.

**Basic Elements of ggplot2:**

**Data**: Raw data to be plotted.

**Geometries (geom_)**: Shapes representing the data.

**Aesthetics (aes())**: Control over appearance like color, size, and shape.

**Scales (scale_)**: Mapping data to aesthetic dimensions.

**Statistical transformations (stat_)**: Summaries of data like quantiles or fitted curves.

**Coordinate system (coord_)**: Mapping data coordinates onto the plot.

**Facets (facet_)**: Arranging data into grid plots.

**Visual themes (theme())**: Setting visual defaults like background and typeface.

## A Default ggplot


